On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-08 paper/paper.tex
Reformat code for single column (and a small typo fix)

\begin{lstlisting}
data ComplexPair where
  ComplexPair :: Complex Double
                 -> Complex Double
                 -> ComplexPair
  deriving (Generic, Show)

@@

  default rep ::
    (ERep (ERepTy t))
    => t -> E t
  rep x = ConstructRep (construct x)
  {-# INLINABLE rep #-}

@@

\begin{lstlisting}
instance (ERep a, ERep b)
  => ERep (Either a b) where

  type ERepTy (Either a b) = Either a b

@@

instance (ERep a, ERep b)
  => ERep (a, b) where

  type ERepTy (a, b) = (a, b)

@@

\begin{lstlisting}
data E t where
  ...
  CaseExp ::
    (ERep t,
     ERepTy (ERepTy t) ~ ERepTy t)
      => ERep t
         -> E (SumMatch (ERepTy t) r)
         -> E r
  ...
\end{lstlisting}

@@

\begin{lstlisting}
isEven' :: Int -> Bool
isEven' =
  internalize (externalize
    (\ eta ->
      runIter (
        \ x ->
          case x == 0 of
            True -> Done True
            False -> case x == 1 of
                True -> Done False
                False -> Step (x - 2))
        eta))
\end{lstlisting}

@@

\begin{lstlisting}
data E t where
  ...
  Lam ::
    (ERep a, Typeable a)
      => Name a -> E b -> E (a -> b)

  Var :: (Typeable a) => Name a -> E a
\end{lstlisting}

>>>>

\begin{lstlisting}
data ComplexPair =
  ComplexPair (Complex Double) (Complex Double)
  deriving (Generic, Show)

@@

  default rep :: (ERep (ERepTy t)) => t -> E t
  rep x = ConstructRep (construct x)

@@

\begin{lstlisting}
instance (ERep a, ERep b) => ERep (Either a b) where
  type ERepTy (Either a b) = Either a b

@@

instance (ERep a, ERep b) => ERep (a, b) where
  type ERepTy (a, b) = (a, b)

@@

\begin{lstlisting}
data E t where
  ...
  CaseExp :: (ERep t, ERepTy (ERepTy t) ~ ERepTy t) =>
    E t -> E (SumMatch (ERepTy t) r) -> E r
  ...
\end{lstlisting}

@@

\begin{lstlisting}
isEven' :: Int -> Bool
isEven' =
  internalize (externalize
    (\ eta ->
      runIter (\ x -> case x == 0 of
                        True -> Done True
                        False -> case x == 1 of
                            True -> Done False
                            False -> Step (x - 2))
              eta))
\end{lstlisting}

@@

\begin{lstlisting}
data E t where
  ...
  Lam :: (ERep a, Typeable a) => Name a -> E b -> E (a -> b)
  Var :: (Typeable a) => Name a -> E a
\end{lstlisting}
